---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hume

<!-- badges: start -->
<!-- badges: end -->

The hume package implements the latent Gaussian and the latent Gaussian copula modeling approaches to learning mixed high dimensional graphs in a fast and easy-to-use manner.  

## Installation

You can install the development version of hume from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("konstantingoe/hume")
```

## Example

The package can be applied on continuous only (then it boils down to the nonparanormal SKEPTIC) and any mix of discrete and continuous variables.

```{r}
library(hume)
library(NHSRdatasets) # load synthetic example dataset 
data(synthetic_news_data)
Omega <- mixed.graph.nonpara(synthetic_news_data, param = 0, names = T) # set additional high-dim penalty to 0
Omega
require(igraph)
# plot from adjacency matrix
plot(graph_from_adjacency_matrix(Omega$`Adjacency Matrix`, mode = "undirected", diag = F),vertex.size=30)
```
